---
title: "Lab 02 - Plastic waste"
author: "Rachel Good"
date: "01/11/2022"
output: github_document
---

## Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

```{r load-data, message=FALSE}
plastic_waste <- read.csv("data/plastic-waste.csv")
```

## Exercises

### Exercise 1

Trinidad and Tobago is a extreme outlier as the carribean islands are one of the world's leading producers of plastic waste.

```{r plastic-waste-continent}
ggplot(data = plastic_waste, aes(x = plastic_waste_per_cap)) +
  geom_histogram(binwidth = 0.2)
plastic_waste %>%
  filter(plastic_waste_per_cap > 3.5)

```

```{r density plot}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent,
                     fill = continent)) +
  geom_density(alpha = 0.7)
```

### Exercise 2

```{r plastic-waste-density}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap, 
                     color = continent,
                     fill = continent)) +
  geom_density(alpha = 0.3)
```

We define color and fill by the mapping aesthetics because we need to assign those qualities to specific variables. On the otherhand, alpha applies to the entire visual and does not need to be changed based on a variable level. 

### Exercise 3
```{r boxplot}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_boxplot()
```


### Exercise 4

```{r violin plot}
ggplot(data = plastic_waste, 
       mapping = aes(x = continent,
                     y = plastic_waste_per_cap,)) +
  geom_violin()
```

The violin plot more clearly displays the density plot for each continent than the density plot shown above. Unlike the boxplot, the violin plot does not clearly show the quartiles, nor the mean of the data set. It also does not have clear points for outliers in the data.


### Exercise 5

Remove this text, and add your answer for Exercise 5 here.

```{r plastic-waste-mismanaged}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap,
                     y = mismanaged_plastic_waste_per_cap,
                     )) +
  geom_point()
```

### Exercise 6

Remove this text, and add your answer for Exercise 6 here.

```{r plastic-waste-mismanaged-continent}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap,
                     y = mismanaged_plastic_waste_per_cap,
                     color = continent,
                     fill = continent)) +
  geom_point()
```

### Exercise 7

Remove this text, and add your answer for Exercise 7 here.

```{r plastic-waste-population-total}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap,
                     y = total_pop,
                     color = continent,
                     fill = continent)) +
  geom_point()
```

```{r plastic-waste-population-coastal}
ggplot(data = plastic_waste, 
       mapping = aes(x = plastic_waste_per_cap,
                     y = coastal_pop,
                     color = continent,
                     fill = continent)) +
  geom_point()
```

### Exercise 8

Remove this text, and add your answer for Exercise 8 here.

```{r recreate-viz}
ggplot(data = plastic_waste, 
       mapping = aes(x = coastal_pop/total_pop,
                     y =  plastic_waste_per_cap,
                     color = continent)) +
  geom_point() +
  ylim(0, 0.7) +
  labs(title = "Plastic waste vs. coastal population proportion",
       subtitle = "by continent",
       x = "Coastal population proportion (Coastal/total population)",
       y = "Plastic waste per capita",
       color = "Continent")
```

## Pro-Tips

### Excercise 3

Try this :D

ggplot(data = plastic_waste, 
       mapping = aes(x = continent, 
                     y = plastic_waste_per_cap)) +
  geom_violin()+
  geom_boxplot(width=.3, fill="green") +
  stat_summary(fun.y=median, geom="point") 
  
### Exercise 5 

Helpful reference:http://www.sthda.com/english/wiki/ggplot2-themes-and-background-colors-the-3-elements



